### 2018-01-26 manuscript.rmd
oriented/orientated debate

---
bibliography: manuscript.bib
csl: molecular-phylogenetics-and-evolution.csl
output:
  pdf_document:
    fig_caption: yes
    includes:
            in_header: mystyles.sty
---

@@

![Schematic of the siphonophore *Nanomia bijuga*, orientated with the anterior of the colony at the top of the page, and the ventral side to the left. Adapted from http://commons.wikimedia.org/wiki/File:Nanomia_bijuga_whole_animal_and_growth_zones.svg, drawn by Freya Goetz. (A) Overview of the whole mature colony. (B) Inset of the pneumatophore and nectosomal growth zone. A series of buds give rise to nectophores. (C) Inset of the siphosomal growth zone. Probuds subdivide to give rise to zooids in repeating-units (cormidia). The gastrozooid (specialized feeding polyp) is the posterior-most zooid within each cormidium.](figures/Figure2.pdf)

>>>>

---
bibliography: manuscript.bib
csl: molecular-phylogenetics-and-evolution.csl
output:
  word_document: default
  pdf_document:
    fig_caption: yes
    includes:
      in_header: mystyles.sty
---

@@

![Schematic of the siphonophore *Nanomia bijuga*, oriented with the anterior of the colony at the top of the page, and the ventral side to the left. Adapted from http://commons.wikimedia.org/wiki/File:Nanomia_bijuga_whole_animal_and_growth_zones.svg, drawn by Freya Goetz. (A) Overview of the whole mature colony. (B) Inset of the pneumatophore and nectosomal growth zone. A series of buds give rise to nectophores. (C) Inset of the siphosomal growth zone. Probuds subdivide to give rise to zooids in repeating-units (cormidia). The gastrozooid (specialized feeding polyp) is the posterior-most zooid within each cormidium.](figures/Figure2.pdf)
